---
title: "p8105_hw1_xz2981"
author: "Xinyan Zhou"
date: "2021/9/25"
output: github_document
---

```{r}
library(tidyverse)
library(palmerpenguins)
```


# Problem 1

## Create the dataframe
```{r}
data_p1 <- tibble(
  norm_samp = rnorm(10,0,1),
  var_logic = norm_samp > 0,
  var_char = "maple glazed donuts",
  var_factor = factor(c("low","low","medium","medium","high","high",
                         "high","high","high","high"))
)
print(data_p1)
```

## Take the mean

The following variables can work:
```{r}
mean(pull(data_p1,norm_samp))
mean(pull(data_p1,var_logic))
```

The following variables cannot work:
```{r}
# mean(pull(data_p1,var_char))
# mean(pull(data_p1,var_factor))
```

When we explicitly convert variables from one type to another, we can take the mean for the following two variables: 
```{r eval = FALSE}
mean(as.numeric(pull(data_p1,var_logic)))
mean(as.numeric(pull(data_p1,var_factor)))
```

Even after converting, we cannot take the mean for var_char.
```{r eval = FALSE}
# mean(as.numeric(pull(data_p1,var_char)))
```


# Problem 2

## Load the dataset
```{r}
data("penguins", package = "palmerpenguins")
summary(penguins)
nrow(penguins)
ncol(penguins)
mean(pull(penguins,flipper_length_mm),na.rm = TRUE)
```

This dataset has 8 variables:
species, factor, three levels-"Adelie","Chinstrap","Gentoo";
island, factor, three levels-"Biscoe","Dream", "Torgersen";
bill_length_mm, numeric, from 32.10 to 59.60, with 2 missing values;
bill_depth_mm, numeric, from 13.10 to 21.50, with 2 missing values;
flipper_length_mm, integer, from 172 to 231, with 2 missing values;
body_mass_g, integer, from 2700 to 6300, with 2 missing values;
sex, factor, 2 levels-"female","male",with 11 missing values;
year, integer, from 2007 to 2009.

The row of the data is 344, and the column is 8.

The mean of flipper length is 200.9152.

## Scatterplot

```{r warning = FALSE, message = FALSE}
penguins %>%
  ggplot(aes(flipper_length_mm,bill_length_mm)) + 
  geom_point(alpha = 0.5, size = 2, aes(color = species)) 

ggsave("penguins.pdf")
```


